### 2016-02-24 ch02-qlogms/excitation-design.tex
Small changes to CH02

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics\TODO{citation} and vibration testing\TODO{citation (ISMA?)} amongst others.

  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion\citep{Oppenheim1983}.
  Therefore the performance of the proposed method is assessed on a prototype system of second order.
  This does not limit the generality of the approach as we can add several of such systems to construct a general \gls{LTI} system.

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis} \citep{FDIDENT}.
    The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.

>>>>

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.

  Any \gls{LTI} system of finite order can be expanded into a finite sum of sub-systems of first and second order by means of a partial fraction expansion~\citep{Oppenheim1983}.
  Therefore the performance of the proposed method is assessed on a prototype system of second order.
  This does not limit the generality of the approach as we can add several of such systems to construct a general \gls{LTI} system.

@@

    For the parametric model, on the other hand, a continuous time \gls{LTI} model of the form
    \begin{equation}
      G(s) = \frac{\Sum_{i=0}^3 b_i s^i}{\Sum_{i=0}^6 a_i s^i}
    \end{equation}
    was estimated using \texttt{elis}~\citep{FDIDENT}.
    The initial estimate was a sixth-order band-pass type I Chebyshev filter \citep{Zverev1967} that conformed to the information given in the datasheet \citep{datasheet_bk1613} to aid convergence to a good optimum.
